Create year end summaries

### 2023-08-31 src/year-end-summary.Rmd
Updated year-end-summary

# Check source
check_source <- function(file_text) {
  message <- NULL
  file_text %>%
    str_subset("^source\\: ") %>%
    str_remove(fixed("source: ")) %>%
    str_remove_all('"')  %>%
    str_remove_all("'") -> file_source
  if (length(file_source)==0) {
    message <- glue("{yy}/{fn} has no source\n")
  }
  if (length(file_source)>1) {
    message <- glue("{yy}/{fn} has multiple sources\n")
  }
  return(message)
}
```

@@

```{r}
# Create links for each file
create_file_list <- function(f, date_list) {
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> short_name
  o <- order(date_list, f)
  glue("+ {date_list[o]} [{short_name[o]}](http://new.pmean.com/{short_name[o]}/)  ") %>%
    paste(collapse="  \n")
}
```

```{r}
# Put it all together
yyyy_list <- c(1999:2023)
n_problems <- 0
n_files <- 0
for (yyyy in yyyy_list) {
  yy <- str_sub(yyyy, 3, 4)
  output_file <- glue("../text/{yy}/{yyyy}.md")
  glue("../text/{yy}") %>%
    list.files %>%
    str_subset("md$") -> f
  problem_files <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{yy}/{fn}"))
    problem_files %<>% append(check_source(file_text))
    date_list %<>% append(check_date(file_text))
  }

  # Update if no problems found
  date_list %>% 
    str_subset(" for ") %>%
    append(problem_files) -> problem_files

  n_year <- length(problem_files)  
  n_problems <- n_problems + n_year
  n_files <- n_files + length(f)
  if (n_year==0) {
    problem_files <- "All files passed date and source quality checks"
  }

  if (n_year > 0) {print(problem_files)}

  cat("\n")
  cat(glue("{yyyy} has a total of {length(f)} files."))
  cat("\n\n")

@@

  create_file_list(f, date_list) %>% write_lines(output_file, append=TRUE)
  write_lines(" ", output_file, append=TRUE)

  problem_files %>% write_lines(output_file, append=TRUE)

  glue("{yyyy}.md created, {length(f)} files, {n_year} problems detected") %>% print
}

print(glue("All years: {n_problems} problems identified in {n_files} files"))
```

>>>>

# Check source
check_source <- function(file_text) {
  file_text %>%
    str_subset("^source\\: ") %>%
    str_remove(fixed("source: ")) %>%
    str_remove_all('"')  %>%
    str_remove_all("'") -> file_source
  if (length(file_source)==0) {
    file_source <- "not listed"
  }
  if (length(file_source)>1) {
    message <- glue("{yy}/{fn} has multiple sources\n")
    file_source <- paste(file_source, collapse=", ")
  }
  message <- glue(", original source is {file_source}.")
  if (tolower(file_source)=="new") message <- "."
  return(message)
}
```

@@

```{r}
# Create links for each file
create_file_list <- function(f, date_list, n_lines, source_files) {
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> short_name
  o <- order(date_list, f)
  glue(
      "+ {date_list[o]} ",
      "[{short_name[o]}]",
      "(http://new.pmean.com/",
      "{short_name[o]}/),  ",
      "{n_lines[o]} lines",
      "{source_files}") %>%
    paste(collapse="  \n")
}
```

```{r}
# Put it all together
yyyy_list <- c(1999:2023)
n_files <- 0
for (yyyy in yyyy_list) {
  yy <- str_sub(yyyy, 3, 4)
  output_file <- glue("../text/{yy}/{yyyy}.md")
  glue("../text/{yy}") %>%
    list.files %>%
    str_subset("md$") -> f
  source_files <- NULL
  date_list <- NULL
  n_lines <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{yy}/{fn}"))
    source_files %<>% append(check_source(file_text))
    date_list %<>% append(check_date(file_text))
    n_lines %<>% append(length(file_text))
  }

  n_files <- n_files + length(f)
  cat("\n")
  cat(glue("{yyyy} has a total of {length(f)} files."))
  cat("\n\n")

@@

  create_file_list(f, date_list, n_lines, source_files) %>% 
    write_lines(output_file, append=TRUE)
  write_lines(" ", output_file, append=TRUE)

  glue("{yyyy}.md created.") %>% print
}

```
